---
title: "Network Golfo San Jorge"
author: "L.A.S."
output: html_document
editor_options: 
  chunk_output_type: console
---

## Setup

```{r setup, eval=TRUE,echo=FALSE }
load(".RData")
#source("R/network_fun.r")

require(igraph)
require(NetIndices)
require(multiweb)
require(stringr)
require(meweasmo)
require(dplyr)
require(ggplot2)
require(future.apply)
require(devtools)
require(doFuture)


```


## GSJ Topological analisis with and without fisheries

**Data Frames** 

websTbl = data.frame with empirical networks


```{r readNetworkCheck, eval=FALSE,echo=F,message=F,warning=F}

# NO FISHING 
#
fileName <- "Data/TTSinPescaInteraccion.dat"

#
# Read Network of posible interactions metaweb
# Prey -> predator 

g <- readNetwork(fileName,edgeListFormat=2) 
# list all vertices
g
E(g)[]
E(g)$weight

# Check POM must have all out none in links
#
V(g)[nei(V(g)[name=="POM"],"out")]
V(g)[nei(V(g)[name=="POM"],"in")]

#
# Check sum of diet for predators must be = 1 
#
B <- as_adj(g,sparse = FALSE,attr = "weight")
BS <- colSums(B)
BS[BS!=1]

# FISHING
#

fileName <- "Data/TTotalInteraccion.dat"    
g1 <- readNetwork(fileName,edgeListFormat=2)
# list all vertices
g1
V(g1)[]

# PESCA must have all in links
#
V(g1)[nei(V(g1)[name=="PESCA"],"out")]
V(g1)[nei(V(g1)[name=="PESCA"],"in")]

#
# Check sum of diet for predators must be = 1 
#
B <- as_adj(g1,sparse = FALSE,attr = "weight")
BS <- colSums(B)
BS[BS!=1]


# Differences between edges NoFishing and Fishing
#
difg <- g1 %m% g 
E(difg)
dfE <- as_long_data_frame(difg)

# Differences between vertex 
setdiff(V(g1)$name,V(g)$name)

plotTrophLevel(g,modules = TRUE)
plotTrophLevel(g1,modules = TRUE)

as.numeric(V(g1)["PESCA"])

#save.image()


```


# Plot networks with numbers 

```{r plotNetworks, eval=FALSE,echo=F,message=T,warning=T}


# UNFISH Plot interactively with numbers

# Names table
g2 <- g
nonf <- tibble(Number=as.numeric(V(g2)),Species=V(g2)$name)   
knitr::kable( nonf )

# Change names to numbers
#
V(g2)$name <- as.numeric(V(g2))
#plotTrophLevel(g2,modules =FALSE ,tk=TRUE, vertexLabel = TRUE,bpal=viridisLite::viridis(11), vertexSizeFactor = 0, vertexSizeMin = 15, vertex.label.color="white")

# Figure supplement S2
#
set.seed(112233)
modw <- spinglass.community(g2)
plotTrophLevel(g2,modules =TRUE ,tk=TRUE, vertexLabel = TRUE,bpal=viridisLite::viridis(11), vertexSizeFactor = 0, vertexSizeMin = 15, vertex.label.color="white",community_obj = modw)

# FISH Plot interactively with numbers
# Names table
g2 <- g1
fish <- tibble(Number=as.numeric(V(g2)),Species=V(g2)$name)   
kk <- left_join(fish,nonf, by="Species")

knitr::kable( kk %>% select(Species, Number.x,Number.y) %>% rename(Fishing=Number.x, Non_fishing=Number.y) )


# Change names to numbers
#
V(g2)$name <- as.numeric(V(g2))
#plotTrophLevel(g2,modules =FALSE ,tk=TRUE, vertexLabel = TRUE,bpal=viridisLite::viridis(11), vertexSizeFactor = 0, vertexSizeMin = 15, vertex.label.color="white")

# Figure supplement S2
#
set.seed(112233)
modw <- spinglass.community(g2)
plotTrophLevel(g2,modules =TRUE ,tk=TRUE, vertexLabel = TRUE,bpal=viridisLite::viridis(11), vertexSizeFactor = 0, vertexSizeMin = 15, vertex.label.color="white",community_obj = modw)


# convert to PNG
#
# convert -colorspace sRGB -density 300 unfished.eps -background white -flatten -resize 1863x2636 -units pixelsperinch -density 224.993 unfished.png



#
# Plot subnetwork of Merluza
#
V(g)$name == "Merluccius hubbsi"
pos <- which(V(g)$name == "Merluccius hubbsi")
g_m <- make_ego_graph(g, nodes=V(g)[pos])
g_m <- g_m[[1]]
nms <- as.numeric(V(g_m)) 
nms[1] <- V(g_m)$name[1]
V(g_m)$name <-  nms
V(g_m)$width = E(g_m)$weight * 100
c <- cluster_infomap(as.undirected(g_m))
plot_troph_level(g_m,modules =TRUE ,tk=TRUE, vertexLabel = TRUE,bpal=viridisLite::viridis(11),vertex.label.color="black", vertexSizeFactor = 20, vertexSizeMin = 10, community_obj = c, edge.width = E(g_m)$weight*10)

#
# Plot subnetwork of PESCA
#
pos <- which(V(g1)$name == "PESCA")
g_m <- make_ego_graph(g1, nodes=V(g1)[pos])
g_m <- g_m[[1]]
nms <- as.numeric(V(g_m)) 
pos <- which(V(g_m)$name == "PESCA")
namesPESCA <- V(g_m)$name
nms[pos] <- V(g_m)$name[pos]
V(g_m)$name <-  nms
V(g_m)$width = E(g_m)$weight * 100
c <- cluster_infomap(as.undirected(g_m))
plot_troph_level(g_m,modules =TRUE ,tk=TRUE, vertexLabel = TRUE,bpal=viridisLite::viridis(11),vertex.label.color="black", vertexSizeFactor = 20, vertexSizeMin = 10, community_obj = c, edge.width = E(g_m)$weight*10)


#
# Plot subnetwork of Mirounga leonina
#
pos <- which(V(g1)$name == "Munida gregaria")
g_m <- make_ego_graph(g1, nodes=V(g1)[pos])
g_m <- g_m[[1]]
nms <- as.numeric(V(g_m)) 
pos <- which(V(g_m)$name == "PESCA")
V(g_m)$width = E(g_m)$weight * 100
c <- cluster_infomap(as.undirected(g_m))
plot_troph_level(g_m,modules =TRUE ,tk=TRUE, vertexLabel = TRUE,bpal=viridisLite::viridis(11),vertex.label.color="black", vertexSizeFactor = 20, vertexSizeMin = 10, community_obj = c, edge.width = E(g_m)$weight*10)

```


## Calc metrics interval confidence using curveBall  


```{r calcMetricsNoFishing14, eval=TRUE,echo=F,message=T,warning=T}

websTbl <- calcTopologicalIndices(g)
websTbl <- bind_cols(websTbl, calc_QSS(g,10000,48, negative = -1, positive = 1)) %>% mutate(Network="noFishing")

lred <- curve_ball(g,1000)
curveBallNets <- calcTopologicalIndices(lred,ncores=48) %>% mutate(Network="noFishing")

tp0 <- calcModularitySWnessZScore(g,lred,ncores=48)
tp <- mutate(tp0$da, Network="noFishing")
wt1 <- inner_join(websTbl,tp)
cb1 <- tp0$sims %>% select(modularity)
curveBallNets <- bind_cols(curveBallNets, cb1)

save.image()

## With Fishing 

tp <- calcTopologicalIndices(g1)
#tp <- bind_cols(tp, calcIncoherence(g1)) 
tp <- bind_cols(tp, calc_QSS(g1,10000,48, negative = -1, positive = 1)) %>% mutate(Network="Fishing")

websTbl <- bind_rows(websTbl, tp)

lred <- curveBall(g1,1000)
tp <- calcTopologicalIndices(lred,ncores=48) %>% mutate(Network="Fishing")
#tp <- bind_cols(tp, calcIncoherence(lred,ncores=48)) %>% mutate(Network="Fishing")

tp0 <- calcModularitySWnessZScore(g1,lred,ncores=48)
tp1 <- mutate(tp0$da, Network="Fishing")
wt2 <- inner_join(websTbl,tp1)

tp <- tp %>% bind_cols(tp0$sims %>% select(modularity))
curveBallNets <- bind_rows(curveBallNets, tp)

websTbl <- bind_rows(wt1,wt2)


rm(cb1,cb2,tp,tp0,wt1,wt2,lred,pf)
save.image()
```


## Calc metrics using diets as weights 

* calc QSS 

```{r calcMetricsDietsQSS, eval=TRUE,echo=F,message=T,warning=T}

#
# Unfished = noFishing
# 
wQSS <- multiweb::calc_QSS(g,10000,48,istrength=TRUE) %>% mutate(Network="noFishing") %>% rename(dietQSS = QSS, dietMEing=MEing)
wQSS <- wQSS %>% bind_rows(multiweb::calc_QSS(g1,10000,48,istrength=TRUE) %>% mutate(Network="Fishing") %>% rename(dietQSS = QSS, dietMEing=MEing))
websTbl <- websTbl %>% inner_join(wQSS)
rm(wQSS)
save.image()
```

* Calculate TL and modularity using BRAND NEW randomizations with weights!!!!!!!!!!!!!!! 

```{r calcMetricsDietsTL, eval=TRUE,echo=F,message=T,warning=T}

weighted_webs <- calc_weighted_topological_indices(g) %>% mutate(Network="noFishing")
lred <- curveBall(g,1000,istrength = TRUE)
tp <- calc_weighted_topological_indices(lred,ncores=48)
tp <- bind_cols(tp, calc_modularity(lred,ncores=48,weights = NULL)) %>% mutate(Network="noFishing")

weighted_CurveBallNets <- tp
rm(tp,lred)
save.image()

weighted_webs <- weighted_webs %>% bind_rows(calc_weighted_topological_indices(g1) %>% mutate(Network="Fishing"))

lred <- curveBall(g1,1000,istrength = TRUE)
tp <- calc_weighted_topological_indices(lred,ncores=48)
tp <- bind_cols(tp, calc_modularity(lred,ncores=48,weights = NULL)) %>% mutate(Network="Fishing")

weighted_CurveBallNets <- bind_rows(weighted_CurveBallNets, tp)
rm(tp,lred)
save.image()

plan(multisession)
wm <- future_lapply(seq_len(100),function(X){
  wm <- calc_modularity(g,weights = NULL) %>% mutate(Network="noFishing")
  wm <- bind_rows(wm,calc_modularity(g1,weights = NULL) %>% mutate(Network="Fishing"))
  })
wm <- bind_rows(wm)

weighted_webs <- weighted_webs %>% inner_join(wm %>% group_by(Network) %>% summarise(wModularity=mean(Modularity)))
rm(wm)

# Update to mean modularity 
#
wm <- future_lapply(seq_len(100),function(X){
  wm <- calc_modularity(g,weights = NA) %>% mutate(Network="noFishing")
  wm <- bind_rows(wm,calc_modularity(g1,weights = NA) %>% mutate(Network="Fishing"))
  })
wm <- bind_rows(wm)


websTbl <- websTbl  %>% select(Network,everything(),-(Modularity:isSWness)) %>% inner_join(wm %>% group_by(Network) %>% summarise(Modularity=mean(Modularity)))

rm(wm,websTbl_new)

knitr::kable(websTbl,digits = 4)

save.image()

```

* WebsTbl
|Network     | Size| Top| Basal| Omnivory| Links|     LD| Connectance| PathLength| Clustering| Cannib| TLmean|  TLmax| LOmnivory| Components| Vulnerability|  VulSD| Generality|  GenSD|    QSS|  MEing| dietQSS| dietMEing| Modularity|
|:-----------|----:|---:|-----:|--------:|-----:|------:|-----------:|----------:|----------:|------:|------:|------:|---------:|----------:|-------------:|------:|----------:|------:|------:|------:|-------:|---------:|----------:|
|Non-fishing |  165|  27|     9|   0.6121|  1015| 6.1515|      0.0373|     0.2093|     0.1503|     13| 2.9572| 4.9361|    0.1727|          1|        7.3551| 1.4463|     6.5064| 1.1072| 0.0546| 0.1066|  0.0962|    0.1644|     0.2885|
|Fishing     |  167|  27|    10|   0.6168|  1084| 6.4910|      0.0389|     0.2008|     0.1618|     13| 2.9086| 4.7999|    0.1824|          1|        7.7429| 1.3907|     6.9045| 1.1665| 0.0276| 0.1265|  0.0729|    0.1507|     0.2825|



* weighted_webs



## Plot metrics interval confidence using curveBall 

```{r plotMetricsCurbeBall, eval=FALSE,echo=F,message=T,warning=T}

# Plots of bivariate 95% confidence ellipses 
#
#curveBallNets <- curveBallNets %>% mutate(Network=if_else(Network=="SanJorgeFishing","Fishing","noFishing"))
require(forcats)
pf <- curveBallNets  %>% group_by(Network) %>% mutate(Network=factor(Network), Network=fct_recode(Network,"Non-fishing"="noFishing"))
pf %>% summarise_if(is.numeric, median) 

websTbl <- websTbl%>% mutate(Network=fct_recode(Network,"Non-fishing"="noFishing","Fishing"="Fished"))
#g2 <- ggplot(pf,aes(Q,color=Network,fill=Network))+ geom_density(alpha=0.2) +  scale_color_viridis_d()+ scale_fill_viridis_d()+theme_bw() + geom_point(data=websTbl[1:2,],aes(Q,0),shape = 21, fill = "white",size=2)
#g2 <- ggplot(pf,aes(Q,color=Network,fill=Network))+ geom_histogram(alpha=0.2) +  scale_color_viridis_d()+ scale_fill_viridis_d()+theme_bw() + geom_point(data=websTbl[1:2,],aes(Q,0),shape = 21, fill = "white",size=2)
# g2 <- ggplot(pf,aes(Q, x=Network,colour=Network))+ geom_jitter(alpha=0.2) +  scale_color_viridis_d()+ theme_bw() +   stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median, geom = "crossbar", size = 0.1,color="Black")+  geom_point(data=websTbl[1:2,],aes(Network,Q),shape = 21, fill = "white",size=2)
# g2

# Filter outliers would be a point below [Q1- (1.5)IQR] or above [Q3+(1.5)IQR].
#
Q <- quantile(pf$TLmean, probs=c(.25, .75), na.rm = FALSE)
iqr <- IQR(pf$TLmean)
pf1 <- pf %>% filter(TLmean<=Q[2]+1.5*iqr,TLmean>=Q[1]-1.5*iqr) 

g1 <- ggplot(pf1,aes(TLmean, x=Network,colour=Network))+ geom_jitter(alpha=0.2) +  scale_color_viridis_d()+ theme_bw() +   stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median, geom = "crossbar", size = 0.1,color="Black") +  geom_point(data=websTbl[1:2,],aes(Network,TLmean),shape = 21, fill = "white",size=2)  + xlab("")
g1


# Filter outliers would be a point below [Q1- (1.5)IQR] or above [Q3+(1.5)IQR].
#

Q <- quantile(pf$LOmnivory, probs=c(.25, .75), na.rm = FALSE)
iqr <- IQR(pf$LOmnivory)
pf1 <- pf %>% filter(LOmnivory<=Q[2]+1.5*iqr,LOmnivory>=Q[1]-1.5*iqr) 

g3 <- ggplot(pf1,aes(LOmnivory, x=Network,colour=Network))+ geom_jitter(alpha=0.2) +  scale_color_viridis_d()+ theme_bw() +   stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median, geom = "crossbar", size = 0.1,color="Black") +  geom_point(data=websTbl[1:2,],aes(Network,LOmnivory),shape = 21, fill = "white",size=2)  + xlab("")  + ylab("Omnivory")
g3


g2 <- ggplot(pf,aes(modularity, x=Network,colour=Network))+ geom_jitter(alpha=0.2) +  scale_color_viridis_d()+ theme_bw() +   stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median, geom = "crossbar", size = 0.1,color="Black") +  geom_point(data=websTbl[1:2,],aes(Network,Modularity),shape = 21, fill = "white",size=2) + xlab("")
g2

require(cowplot)

gg <- plot_grid(g1 + theme(legend.position="none"),
                g2 + theme(legend.position="none"),
                g3 + theme(legend.position="none"),align = "h",ncol=3)

gg
# add the legend to the row we made earlier. Give it one-third of the width
# of one plot (via rel_widths).
# p <- plot_grid( gg, get_legend(g2+theme(legend.position="bottom")), ncol=1,rel_heights = c(1, .2))
# p
# save_plot("Figures/curveBall_metrics.png",gg,base_width=8,base_height=5,dpi=600)


#
# Calculates the Anderson-Darling Test and median diff effect size
#

require(kSamples)
require(tidyr)
require(purrr)

df <- curveBallNets %>% dplyr::select(TLmean,LOmnivory,modularity) %>% map(~ad.test(. ~ Network, data=curveBallNets)) %>% map_df(~.$ad[1,])
knitr::kable(df)

df <- curveBallNets %>% group_by(Network) %>% dplyr::select(TLmean,LOmnivory,modularity) %>% summarize_if(is.numeric, median)  %>% gather("metric","medianDif" ,-Network) %>% group_by(metric) %>% summarize_if(is.numeric,~diff(.))

df1 <- curveBallNets %>% dplyr::select(Network,TLmean,LOmnivory,modularity) %>% gather("metric","value" ,-Network) %>%   group_by(metric) %>% summarize(sdM = sd(value))

df2 <- curveBallNets %>% group_by(Network) %>% dplyr::select(TLmean,LOmnivory,modularity) %>% summarize_if(is.numeric, median) %>%  gather("metric","median" ,-Network) %>%  spread(Network,median)

dfu <- inner_join(df,df1)  %>% inner_join(df2) %>% mutate(effectSize=medianDif/sdM) %>% arrange(effectSize) %>%  mutate(type="Unweighted")

knitr::kable(dfu,digits = 4)


#
# Confidence interval for QSS
#
require(binom)
df <- websTbl %>% dplyr::select(Network,QSS) %>% group_by(Network) %>% do( binom.confint(.$QSS*10000, 10000,methods = "wilson")) %>% mutate(type="Unweighted")

prop.test(x=websTbl$QSS*10000, n=c(10000,10000))

ggplot(df, aes(Network,mean,color=Network)) + geom_point() + geom_errorbar(aes(ymin=lower,ymax=upper),width=0.2) + scale_color_viridis_d()+ theme_bw() + ylab("Quasi sign stability")+ guides(color="none")
#ggsave("Figures/QSS.png",width=6,height=5,units="in",dpi=600)

#
# Confidence interval for diet QSS
#
require(binom)
df1 <- websTbl %>% dplyr::select(Network,dietQSS) %>% group_by(Network) %>% do( binom.confint(.$dietQSS*10000, 10000,methods = "wilson")) %>% mutate(type="Weighted")

prop.test(x=websTbl$dietQSS*10000, n=c(10000,10000))

ggplot(df, aes(Network,mean,color=Network)) + geom_point() + geom_errorbar(aes(ymin=lower,ymax=upper),width=0.2) + scale_color_viridis_d()+ theme_bw() + ylab("Weighted Quasi sign stability")+ guides(color="none")
#ggsave("Figures/dietQSS.png",width=6,height=5,units="in",dpi=600)

require(forcats)
df <- bind_rows(df,df1) 
#df <- df %>% mutate(Network=fct_recode(Network,Unfished="noFishing",Fished="Fishing"))
ggplot(df, aes(Network,mean,color=Network)) + geom_point() + geom_errorbar(aes(ymin=lower,ymax=upper),width=0.2) + scale_color_viridis_d()+ theme_bw() + facet_wrap( ~type)+ guides(color="none") + ylab("Quasi sign stability")
ggsave("Figures/QSS.png",width=6,height=5,units="in",dpi=600)

```


## Topological

|     AD|   T.AD|  asympt. P-value|
|------:|------:|----------------:|
| 594.28| 779.94|                0| TLmean
| 326.49| 427.91|                0| LOmnivory
| 614.56| 806.62|                0| modularity


|metric     | medianDif|    sdM| Fishing| noFishing| effectSize|type       |
|:----------|---------:|------:|-------:|---------:|----------:|:----------|
|LOmnivory  |   -0.0094| 0.1017|  0.1862|    0.1768|    -0.0921|Unweighted |
|TLmean     |    0.0488| 0.0879|  2.9118|    2.9606|     0.5546|Unweighted |
|modularity |    0.0063| 0.0041|  0.2807|    0.2870|     1.5494|Unweighted |

## QSS 

	2-sample test for equality of proportions with continuity correction

data:  websTbl$QSS * 10000 out of c(10000, 10000)
X-squared = 91.804, df = 1, p-value < 2.2e-16
alternative hypothesis: two.sided
95 percent confidence interval:
 0.0214101 0.0325899
sample estimates:
prop 1 prop 2 
0.0546 0.0276 


## Weigthed QSS

	2-sample test for equality of proportions with continuity correction

data:  websTbl$dietQSS * 10000 out of c(10000, 10000)
X-squared = 34.769, df = 1, p-value = 3.712e-09
alternative hypothesis: two.sided
95 percent confidence interval:
 0.01549529 0.03110471
sample estimates:
prop 1 prop 2 
0.0962 0.0729 


## Plot weighted metrics interval confidence using curveBall 

```{r plotWeightedMetricsCurbeBall, eval=FALSE,echo=F,message=T,warning=T}

# Plots of bivariate 95% confidence ellipses 
#
#curveBallNets <- curveBallNets %>% mutate(Network=if_else(Network=="SanJorgeFishing","Fishing","noFishing"))
require(forcats)
pf <- weighted_CurveBallNets  %>% group_by(Network) %>% mutate(Network=factor(Network), Network=fct_recode(Network,"Non-fishing"="noFishing"))
pf %>% summarise_if(is.numeric, median) 

weighted_webs <- weighted_webs %>% mutate(Network=fct_recode(Network,"Non-fishing"="noFishing"))


# Filter outliers would be a point below [Q1- (1.5)IQR] or above [Q3+(1.5)IQR].
#
Q <- quantile(pf$wTLmean, probs=c(.25, .75), na.rm = FALSE)
iqr <- IQR(pf$wTLmean)
pf1 <- pf %>% filter(wTLmean<=Q[2]+1.5*iqr,wTLmean>=Q[1]-1.5*iqr) 

g4 <- ggplot(pf1,aes(wTLmean, x=Network,colour=Network))+ geom_jitter(alpha=0.2) +  scale_color_viridis_d()+ theme_bw() +   stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median, geom = "crossbar", size = 0.1,color="Black")+  geom_point(data=weighted_webs[1:2,],aes(Network,wTLmean),shape = 21, fill = "white",size=2) + ylab("Weigthed TLmean") + xlab("")
g4

g5 <- ggplot(pf,aes(Modularity, x=Network,colour=Network))+ geom_jitter(alpha=0.2) +  scale_color_viridis_d()+ theme_bw() +   stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median, geom = "crossbar", size = 0.1,color="Black") +  geom_point(data=weighted_webs[1:2,],aes(Network,wModularity),shape = 21, fill = "white",size=2) + xlab("") + ylab("Weigthed Modularity")
g5

# Filter outliers would be a point below [Q1- (1.5)IQR] or above [Q3+(1.5)IQR].
#
Q <- quantile(pf$wLOmnivory, probs=c(.25, .75), na.rm = FALSE)
iqr <- IQR(pf$wLOmnivory)
pf1 <- pf %>% filter(wLOmnivory<=Q[2]+1.5*iqr,wLOmnivory>=Q[1]-1.5*iqr) 

g6 <- ggplot(pf1,aes(wLOmnivory, x=Network,colour=Network))+ geom_jitter(alpha=0.2) +  scale_color_viridis_d()+ theme_bw() +   stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median, geom = "crossbar", size = 0.1,color="Black") +  geom_point(data=weighted_webs[1:2,],aes(Network,wLOmnivory),shape = 21, fill = "white",size=2)  + xlab("") + ylab("Weigthed Omnivory")

g6

require(cowplot)
gg <- plot_grid(g1 + theme(legend.position="none"),
                g2 + theme(legend.position="none"),
                g3 + theme(legend.position="none"),
                g4 + theme(legend.position="none"),
                g5 + theme(legend.position="none"),
                g6 + theme(legend.position="none"),align = "h",ncol=3)

gg

# add the legend to the row we made earlier. Give it one-third of the width
# of one plot (via rel_widths).
# p <- plot_grid( gg, get_legend(g2+theme(legend.position="bottom")), ncol=1,rel_heights = c(1, .2))
# p
save_plot("Figures/weighed_curveBall_metrics.png",gg,base_width=8,base_height=6,dpi=600)


require(kSamples)
require(tidyr)
require(purrr)

df <- weighted_CurveBallNets %>% dplyr::select(wTLmean,wLOmnivory,Modularity) %>% map(~ad.test(. ~ Network, data=weighted_CurveBallNets)) %>% map_df(~.$ad[1,])
knitr::kable(df)

df <- weighted_CurveBallNets %>% group_by(Network) %>% dplyr::select(wTLmean,wLOmnivory,Modularity) %>% summarize_if(is.numeric, median)  %>% gather("metric","medianDif" ,-Network) %>% group_by(metric) %>% summarize_if(is.numeric,~diff(.))

df1 <- weighted_CurveBallNets %>% dplyr::select(Network,wTLmean,wLOmnivory,Modularity) %>% gather("metric","value" ,-Network) %>%   group_by(metric) %>% summarize(sdM = sd(value))

df2 <- weighted_CurveBallNets %>% group_by(Network) %>% dplyr::select(wTLmean,wLOmnivory,Modularity) %>% summarize_if(is.numeric, median) %>%  gather("metric","median" ,-Network) %>%  spread(Network,median)

dfw <- inner_join(df,df1)  %>% inner_join(df2) %>% mutate(effectSize=medianDif/sdM) %>% arrange(effectSize) %>% mutate(type="Weighted")

#
# Add unweighted and weighted
#
dfw <- bind_rows(dfu,dfw) %>% select( type, everything())
knitr::kable(dfw,digits = 4)





```

* Anderson Darling / effect Size

|     AD|   T.AD|  asympt. P-value|
|------:|------:|----------------:|
| 556.22| 729.92|                0|
| 554.04| 727.04|                0|
| 154.63| 201.96|                0|


|metric     |  medianDif|       sdM|    Fishing|  noFishing| effectSize|
|:----------|----------:|---------:|----------:|----------:|----------:|
|wTLmean    | -0.0911413| 0.2490611|  3.0445255|  2.9533842| -0.3659394|
|wLOmnivory | -0.0595303| 1.1041427|  0.2234628|  0.1639325| -0.0539154|
|Modularity |  0.8695713| 1.1809291| -5.3771676| -4.5075963|  0.7363451|

## Weighted 


|      AD|   T.AD|  asympt. P-value|
|-------:|------:|----------------:|
| 323.820| 424.40|                0| wTLmean
|  78.797| 102.27|                0| wLOmnivory
|  87.164| 113.27|                0| Modularity

|metric     |  medianDif|       sdM|    Fishing|  noFishing| effectSize|
|:----------|----------:|---------:|----------:|----------:|----------:|
|wLOmnivory | -0.0130452| 0.1239900|  0.1756424|  0.1625972| -0.1052114|
|Modularity |  0.4885215| 0.9860427| -4.9992604| -4.5107388|  0.4954365|
|wTLmean    |  0.0517255| 0.1012028|  2.9020820|  2.9538074|  0.5111070|


# Keystoneness centrality

```{r centrality, eval=FALSE,echo=F,message=T,warning=T}

k_no_fish <- degree(g)
k_no_fish <- tibble(species=names(k_no_fish),degree=k_no_fish) %>% arrange(desc(degree))

k_fish <- degree(g1)
k_fish <- tibble(species=names(k_fish),degree=k_fish) %>% arrange(desc(degree))

kk <- left_join(k_fish,k_no_fish, by="species")
names(kk) <- c("Species","Fishing","Nonfishing")
#kk <- kk %>% filter(Fishing != Nonfishing)
knitr::kable(kk)
pander::pandoc.table(kk[1:23,],digits = 4,style="rmarkdown",emphasize.italics.cols=1 )
  

# Weighted degree (not too much sense with diets)
#
# k_no_fish <- strength(g)
# k_no_fish <- tibble(species=names(k_no_fish),Strength=k_no_fish) %>% arrange(desc(Strength))
# k_fish <- strength(g1)
# k_fish <- tibble(species=names(k_fish),Strength=k_fish) %>% arrange(desc(Strength))
# kk1 <- left_join(k_fish,k_no_fish, by="species")
# names(kk1) <- c("Species","Fished","Unfished")
# 
# knitr::kable(kk1)

# Trophic level 

tl_no_fish <- NetIndices::TrophInd(get.adjacency(g,sparse=F))
tl_no_fish <- tibble(species=rownames(tl_no_fish),TL=tl_no_fish$TL) %>% arrange(desc(TL))
tl_fish <- NetIndices::TrophInd(get.adjacency(g1,sparse=F))
tl_fish <- tibble(species=rownames(tl_fish),TL=tl_fish$TL) %>% arrange(desc(TL))
kk1 <- left_join(tl_fish,tl_no_fish, by="species")
names(kk1) <- c("Species","Fished","Unfished")
mean(kk1$Fished)
mean(kk1$Unfished, na.rm = TRUE)

knitr::kable(kk1,digits = 4)
pander::pandoc.table(kk1,digits = 4,style="rmarkdown",emphasize.italics.cols=1 )

# Table with TL of PESCA Preys
#
namesPESCA <- namesPESCA[-c(48)]

knitr::kable(kk1 %>% filter(Species %in% namesPESCA))
# Average trophic level of PESCA
#
kk1 %>% filter(Species %in% namesPESCA) %>% summarise_all(mean,na.rm = TRUE)
  
```



